R for Clinical Study Reports and Submission

### 2021-10-12 project-folder.Rmd
project-folder.Rmd edited online with Bitbucket

To deliver the A&R results of a clinical trial project, it is teamwork that typically requires collaborations from both statisticians and programmers. 
In this part, let's consider how to organize a clinical trial project as an A&R leader.

>>>>

To deliver the A&R results of a clinical trial project, 
it is a teamwork that typically requires collaborations from both statisticians and programmers. 
In this part, let's consider how to organize a clinical trial project as an A&R leader.
